Ross Adam:

\begin{itemize}
\item Organised Presentation
\item Contributed to Introduction section of dissertation
\item Contributed to Background section of dissertation
\item Contributed to Design section of dissertation
\item Contributed to Evaluation section of the dissertation
\item Managed team as Project Manager
\end{itemize}

Andrew Gardner:

\begin{itemize}
\item Contributed to initial direction of project 
\item Contributed to requirements gathering of project
\item Contributed to design of project
\item Contributed to implementation of project
\item Contributed to Design section of dissertations
\item Liaised with client as Customer Liaison
\end{itemize}

Nicole Kearns:

\begin{itemize}
\item Secretary for the team.
\item Communications with the client, Dr Fiona Dowell.
\item Contributed to the initial direction of project.
\item Contributed to the initial design of the project.
\item Contributed to the requirements gathering of the project.
\item Contributed to the Introduction section of the dissertation.
\item Contributed to the Background section of the dissertation.
\item Contributed by writing the Requirements section of the dissertation.
\item Contributed by writing the Testing and Evaluation section of the dissertation.
\item Contributed to the Conclusion section on the dissertation.
\item Contirbuted to the evaluation process of the project.
\end{itemize}

Mamas Nicolaou
\begin{itemize}
\item Contributed to the initial direction of project.
\item Contributed to the initial design of the project.
\item Contributed by creating the Django Models for the Project.
\item Contributed by creating the Django Views for the Project.
\item Contributed by creating the Django URL Dispatched for the Project.
\item Contributed by implementing the Django templates.
\item Contributed by resolving bugs raised by other team members.
\item Contributed by creating the Administration Interface for the Project.
\item Contributed by writing the Implementation section of the dissertation.
\item Contributed by creating the Final Assessment, Topic, Contents pages.
\item Contributed to the Testing and Evaluation section of the dissertation.
\end{itemize}

Asset Sarsengaliyev
\begin{itemize}
\item Contributed to design of project
\item Contributed to design implementation of project

\end{itemize}
